---
title: "TDSC"
author: "Rohan"
date: "October 8, 2016"
output: 
---

```{r}
setwd("TDSC")
data<- read.csv("transaction_data_8451.csv")
eggs <- data[which(data$COMMODITY_DESC == 'EGGS'),]
# Probability that a household has bought eggs 
egg_baskets <- sum(unique(eggs$BASKET_ID))
all_baskets <- sum(unique(data$BASKET_ID))
prob_eggs_basket <- egg_baskets/all_baskets
egg_hh <- sum(unique(eggs$household_key))
all_hh <- sum(unique(data$household_key))
prob_eggs_hh <- egg_hh/all_hh
households = unique(data$household_key)
commodities <- as.character(unique(data$COMMODITY_DESC))
baskets = unique(data$BASKET_ID)
```

```{r}
# Complementary Commodities
freq_bought = rep(0,length(commodities))
freq_boughtwitheggs = rep(0,length(commodities))
prob_boughtwitheggs = rep(0,length(commodities))
freq_comps <- cbind(commodities,freq_bought,freq_boughtwitheggs,prob_boughtwitheggs)
for(i in 1:length(commodities)) {
  comm = commodities[i]
  num_baskets_in = 0
  num_baskets_in_with_eggs = 0
  subbasket = data[which(data$COMMODITY_DESC == comm),]
  num_baskets_in = nrow(subbasket)
  baskid = unique(subbasket$BASKET_ID)
  for(k in 1:length(baskid)) {
    id = baskid[k]
    if('EGGS' %in% data[which(data$BASKET_ID == id),'COMMODITY_DESC']) {
      num_baskets_in_with_eggs = num_baskets_in_with_eggs+1
    }
  }
  freq_comps[i,2] = as.numeric(num_baskets_in)
  freq_comps[i,3] = as.numeric(num_baskets_in_with_eggs)
  freq_comps[i,4] = as.numeric(freq_comps[i,3])/as.numeric(freq_comps[i,2])
}
write.csv(freq_comps,'Complementary Goods')
```

```{r}
# HH Size, P(eggs|size)
sizes = c(1,2,3,4,5)
freq = rep(0,5)
eggs_freqbysize = rep(0,5)
prob_hhsize_eggs= rep(0,5)
freq_sizes = cbind(sizes,freq,eggs_freqbysize,prob_hhsize_eggs)
for (h in 1:length(households)){
  hhsize = data[which(data$household_key == households[h]),"HOUSEHOLD_SIZE_DESC"][1]
  if (!is.na(hhsize)) {
    if(hhsize == '5+') 
      hhsize = 5
    freq_sizes[hhsize,2] = freq_sizes[hhsize,2]+1
    if(households[h] %in% eggs$household_key)
      freq_sizes[hhsize,3] = freq_sizes[hhsize,3]+1   
  }
}
for(i in 1:5) {
  freq_sizes[i,4] = freq_sizes[i,3]/freq_sizes[i,2]
}
write.csv(freq_sizes,'HH_freqs')
```

```{r} 
# Loyalty
loy_subset = data[which(data$LOY_CARD_DISC != 0.00),]
length(unique(loy_subset$household_key))
savings <- ((data$BASE_SPEND_AMT-data$NET_SPEND_AMT)/data$BASE_SPEND_AMT)*100
data <- cbind(data,savings)
data[which(is.na(data$savings)),] = 0
data[which(data$savings < 0),] = 0
eggs = data[which(data$COMMODITY_DESC == 'EGGS'),]
noteggs = data[which(data$COMMODITY_DESC != 'EGGS'),]
# Difference between savings of egg-buyers and not egg-buyers 
mean(eggs$savings) - mean(noteggs$savings)
# "People who buy eggs save on average 5.788% less"
```

```{r}
# Independence tests: how close 
```

```{r}

prob_in_basket_with_eggs <= data.frame()
cbi





#for (i in 1:length(households)) {
  household = data[which(data$household_key == households[i]),]
  
  num_baskets = length(baskets)
  count_egg_and_comm = 0
  #for(basket in num_baskets) {
    bask = household[which(household$BASKET_ID == baskets[i])]
    commodities = unique(bask$COMMODITY_DESC)
   # for (comm in commodities){
      numbasketscomIn
    #  if ('EGGS' %in% bask$COMMODITY_DESC) {
        count_egg_and_comm <- count_egg_and_comm + 1
  #      }
        
 # }  
#}
```


# HH Income, P(eggs|income)
incomes = c(1,2,3,4,5,6,7,8,9,10,11,12)
freq = rep(0,12)
eggs_freqbyincome = rep(0,12)
prob_hhincome_eggs= rep(0,12)
freq_incomes = cbind(incomes,freq,eggs_freqbyincome,prob_hhincome_eggs)
for (h in 1:length(households)){
  hhincome = data[which(data$household_key == households[h]),"INCOME_DESC"][1]
  if (!is.na(hhincome)) {
    if(hhincome == 'Under 15K') 
      hhincome = 1
    if(hhincome == '15-24K') 
      hhincome = 2
    if(hhincome == '25-34K') 
      hhincome = 3
    if(hhincome == '35-49K') 
      hhincome = 4
    if(hhincome == '50-74K') 
      hhincome = 5
    if(hhincome == '75-99K') 
      hhincome = 6
    if(hhincome == '100-124K') 
      hhincome = 7
    if(hhincome == '125-149K') 
      hhincome = 8
    if(hhincome == '150-174K') 
      hhincome = 9
    if(hhincome == '175-199K') 
      hhincome = 10
    if(hhincome == '200-249K') 
      hhincome = 11
    if(hhincome == '250K+') 
      hhincome = 12
    freq_incomes[hhincome,2] = freq_incomes[hhincome,2]+1
    if(households[h] %in% eggs$household_key)
      freq_incomes[hhincome,3] = freq_incomes[hhincome,3]+1   
  }
}
for(i in 1:12) {
  freq_incomes[i,4] = freq_incomes[i,3]/freq_incomes[i,2]
}
write.csv(freq_incomes,'HHI_freqs')


